### 2009-10-21 doc/tech_doc/jura/jura-tech-doc.tex
Documenting JURA interactive mode, correcting refs in PDF

\verb|jura [-E <expiration_time>] <control_dir> [<control_dir> [...]]|

@@

@@

After successful submission to a reporting destination, the job log
file is deleted, preventing multiple insertion of usage records. If
submission fails, the log files are kept, so another attempt is made
upon a subsequent run of JURA. This can repeat until the expiration
time passes (see ``\textit{-E}'' command line switch in Section
\ref{exec}), at which point the next execution of JURA removes the
file without processing.
%TODO archiving

@@

\subsection{Reporting to LUTS}
\label{accessing}
The generated URs are submitted to the accounting services specified
by the reporting destination configuration parameters and if present,
to the destinations specified in the job description as
well. Reporting URs to several destinations is possible, but currently
only SGAS LUTS destinations are supported.

@@

\begin{itemize}
%\item An archiving functionality, storing generated URs in a local
%  directory specified in the configuration.
\item Support for other accounting systems besides LUTS, especially
  the EGEE Accounting Service. However, appropriate documentation on
  the service interfaces is missing as of now.
\item Extend JURA to be able to read all necessary parameters
  (credentials, reporting targets) from the command line so that it
  can serve as a stand-alone reporting utility invoked independently
  from A-REX.
\item Enable generating coarser-grained ``\textit{Aggregate URs}''
  from multiple URs.
\item Investigate the subject of project-related charging: who is
  responsible for determining the ``\textit{charge}'' value; what rules should
  be applied?
\end{itemize}

>>>>

\verb|jura [-E <expiration_time>] [-u <url> [-u <url> [...]]] <control_dir> [<control_dir> [...]]|

@@

The ``\textit{-u}'' option can be used for interactive execution
(e.g.~from a terminal). In this case, usage data generated for each
job is reported once to each of the specified destination URLs
regardless of the content of the job log files, and no job log files
are deleted.

@@

If interactive mode is not activated by the ``\textit{-u}'' option
(see Section \ref{exec}),
after successful submission to a reporting destination, the job log
file is deleted, preventing multiple insertion of usage records. If
submission fails, the log files are kept, so another attempt is made
upon a subsequent run of JURA. This can repeat until the expiration
time passes (see ``\textit{-E}'' command line switch in Section
\ref{exec}), at which point the next execution of JURA removes the
file without processing.
%TODO archiving

@@

\subsection{Reporting to LUTS}
\label{accessing}
In case of non-interactive invocation of JURA by A-REX, 
the generated URs are submitted to the accounting services specified
by the reporting destination configuration parameters and if present,
to the destinations specified in the job description as
well. Under interactive mode of operation, they are submitted to the
services given via the ``\textit{-u}'' command line option. Reporting
URs to several destinations is possible, but currently
only SGAS LUTS destinations are supported.

@@

\begin{itemize}
%\item An archiving functionality, storing generated URs in a local
%  directory specified in the configuration.
\item Support for other accounting systems besides LUTS, especially
  the EGEE Accounting Service. However, appropriate documentation on
  the service interfaces is missing as of now.
\item Extend JURA to be able to read credentials from the command line
  in interactive mode.
\item Enable generating coarser-grained ``\textit{Aggregate URs}''
  from multiple URs.
\item Investigate the subject of project-related charging: who is
  responsible for determining the ``\textit{charge}'' value; what rules should
  be applied?
\end{itemize}
